The Unintended Consequences of Energy Reduction

### 2024-02-15 paper/paper.qmd
Formatted figures for the pdf

![Figure 1](../other/figures/figure1.png)
![Figure 3](../other/figures/figure3.png)
![Figure 4](../other/figures/figure4.png)
After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts. While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days. Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95)[figure 3]. In addition, the mortality rate for heatstrokes also increased dramatically in the year 2011 more than doubling that of 2010.
Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted. To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy. Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.).
Lastly, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et. al).

@@

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

@@

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

![Relative Energy Consumption and Price](../other/figures/figure1.png){#fig-energy}

![Mortality Rate and Policy](../other/figures/figure3.png){#fig-mortality}

![Number of Heatstroke Incidents from 2008 to 2015](../other/figures/figure4.png){#fig-heatstrokeIncidents}

After the Fukushima incident, the government tried to ensure sufficient backup capacity to avoid power blackouts. While other factors could affect the saving target, the primary determinant of the saving target was a region’s dependence on nuclear power before the accident.(Kim, et al.) This caused more health issues for individuals as they were encouraged to not use AC and other cooling devices during hotter days. Previous to the implementation of the energy policy, throughout the period between 1960 and 2004, the mortality rate was significantly lower (closer to 0.87) while the mortality rate after was much higher (close to 0.95)[figure 3]. In addition, the mortality rate for heatstrokes also increased dramatically in the year 2011 more than doubling that of 2010.
Moreover, the mortality risk caused by electricity saving is particularly high in the summer, during which the energy-saving campaigns are intensively promoted. To account for the potential “harvesting effect” or “delayed effect,” we also estimate distributed lag models on the impacts of temperature and the energy-saving policy. Taking into account this dynamic impact, it is estimated that the energy-saving campaigns could have led to nearly 7,710 premature deaths annually in Japan (Kim, et al.).
Lastly, there is a trend where the higher the saving targets, the higher the increase in the mortality rate during the hot days (between 25–30°C and above 30°C), but a relatively moderate increase for cold temperatures (below 0°C and 0–5°C) (Kim et. al).

@@

@@
